Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-08-30 paper/ms.tex
Update figure placements
Small updates

% Abstract of the paper
\begin{abstract}
Elongated bar-like features are ubiquitous in galaxies, occurring at the centers
of approximately two-thirds of spiral disks.  Due to gravitational interactions
between the bar and the other components of galaxies, it is expected that
angular momentum and matter will redistribute over long (Gyr) timescales in
barred galaxies. Previous work ignoring the gas phase of galaxies has
conclusively demonstrated that bars should slow their rotation over time due to
their interaction with dark matter halos. We have performed a simulation of a
Milky Way-like galactic disk hosting a strong bar which includes a
state-of-the-art model of the interstellar medium and a live dark matter halo.
In this simulation the bar pattern does not slow down over time, and instead
remains at a stable, constant rate of rotation. This behavior has been observed
in previous simulations using more simplified models for the interstellar gas
but the apparent lack of secular evolution has remained unexplained. We propose
that the gas phase of the disk and the dark matter halo act in concert to
stabilize the bar pattern speed and prevent the bar from slowing down or
speeding up. We find that in a Milky Way-like disk, a gas fraction of only about
5\% is necessary for this mechanism to operate. Our result naturally explains
why nearly all observed bars rotate rapidly and is especially relevant for our
understanding of how the Milky Way arrived at its present state.
\end{abstract}

@@

We have performed a simulation of a disk galaxy using the finite-volume,
gravito-hydrodynamics code AREPO \citep{2010MNRAS.401..791S}. We use the galaxy
formation model Stars and MUltiphase Gas in GaLaxiEs
\citep[SMUGGLE;][]{2019MNRAS.489.4233M}. This disk galaxy exhibits almost no
evolution in the bar pattern speed over several Gyr when the gas phase is
accounted for and properly modeled. This behavior has been observed in a few
previous works \citep{1993AA...268...65F, 2010ApJ...719.1470V,
2014MNRAS.438L..81A}. However, we are the first to demonstrate that the behavior
ought to be present in a large fraction of galaxies, since it occurs in our
simulation with gas fractions as low as about $5\%$. We are also the first to
provide a physical explanation of the behavior with clear observational
predictions.

@@

As we saw qualitatively in Fig.~\ref{fig:overview}, the middle panel of
Fig.~\ref{fig:strength} shows that the length of the bar in the \Nbody{} case
grows over time while it remains roughly constant in the SMUGGLE case. This is
also consistent with previous numerical work, which found that bars tend to grow
as they slow down and the radius of corotation increases
\citep{2000ApJ...543..704D, 2003MNRAS.341.1179A}. The time evolution of the bar
strength, defined as the maximum of $\left|A_2/A_0\right|$ as a function of
radius, is shown in the lower panel Fig.~\ref{fig:strength}. The quantity
$\left|A_2/A_0\right|$ varies from $0$ to $1$, with larger values indicating a
stronger bar pattern. We see that in the \Nbody{} case, $\left|A_2/A_0\right|$
increases over time as the bar pattern slows. This is consistent with previous
\Nbody{} simulations which showed a clear correlation between the bar pattern
speed and the bar strength \citep[e.g.,][]{2003MNRAS.341.1179A}. In the SMUGGLE
case, we see that the bar strength has an initial drop but then remains at a
roughly constant, but slightly decreasing, strength. This is consistent with the
pattern speed in the SMUGGLE case being roughly constant or slightly increasing.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Pattern Speed Evolution}
The lack of evolution in the pattern speed of the SMUGGLE case (seen in
Fig.~\ref{fig:prop}) is intimately tied to the sudden decrease in torque exerted
on the bar by the dark matter halo. We argue that this can be understood in
terms of the halo wake mechanism. In the \Nbody{} case, halo material that is
resonant with the bar will form a wake which lags behind and exerts a negative
torque on the bar, slowing it down \citep{1984MNRAS.209..729T,
1985MNRAS.213..451W, 1992ApJ...400...80H}.\footnote{Since the bar is not a solid
body, it is not guaranteed that a negative torque will slow it down - e.g. a
negative torque could shred the bar, reducing its moment of inertia without
changing its pattern speed. However, the bar seems to empirically respond to a
negative torque induced by a halo wake by slowing down.} As the bar slows down,
the location of the resonances in phase space changes, allowing halo material
newly resonant with the bar to participate in forming the wake. However, the gas
is a reliable source of positive torque on the bar, speeding the bar up. This
stops the resonance location from changing such that the halo cannot reinforce
the wake, arresting the process by which the halo can slow the bar down. We term
this process ``exhaustion.''

@@

We argue that the following occurs. First, the bar is not able to slow down
quickly enough due to the positive torque of the infalling gas. This causes
the resonant halo phase space at a particular pattern speed, $\Omega_{p,0}$,
to become exhausted and no longer able to support a negative torque. Second,
the gas is still exerting a positive torque on the bar, and therefore the
pattern speed will again increase. Since at higher pattern speeds the halo has
not yet been totally exhausted, the halo will once again be able to exert a
negative torque on the bar. The pattern speed will then settle at a new value
slightly higher than $\Omega_{p,0}$ where the gas and halo torques cancel.
Over time, the pattern speed should slowly increase as the halo becomes
progressively exhausted.

@@

\subsection{Varying Initial Gas Fractions}
We also performed a test in which we varied the initial gas fraction of the
disk. In our fiducial run, we set the surface density of the gas disk from
$4\,\textrm{kpc}$ to $\sim9.3\,\textrm{kpc}$ to be $20\,\Msun/\textrm{pc}^2$.
We also ran with surface densities of $15$, $10$, and
$5\,\Msun/\textrm{pc}^2$. These correspond to initial gas fractions of
approximately $16\%$, $10\%$, $7\%$, and $4\%$. The pattern speed evolution is
shown in Fig.~\ref{fig:fgas} We find that the bar in disks with
initial surface densities of $20$, $15$, and $10\,\Msun/\textrm{pc}^2$ evolve
with a constant pattern speed while the bar in a disk with initial surface
density of $5\,\Msun/\textrm{kpc}^2$ slows down at a similar rate to the \Nbody{} case.

@@

\subsection{Smooth Interstellar Medium}
We also performed a simulation of the same disk but with a simpler model of the
interstellar medium \citep{2003MNRAS.339..289S}, closer to standard methods used
in cosmological simulations of galaxy formation and described in more detail in
Section~\ref{sec:methods}. The result of this test is presented in
Fig.~\ref{fig:GFM}. We find that the pattern speed evolution is nearly the same
in this case, and so conclude that our result is not sensitive to the details of
the model for the interstellar medium.

@@

We allow the bar in this model to rotate as a solid body. However, we crucially
allow the pattern speed of the bar to freely change with time in accordance with
the torque exerted on the dark matter halo by the bar. In particular, we
subtract the $z$-component of this torque divided by the moment of inertia of
the bar from the pattern speed. Since the radius of corotation \RCR{} is a
parameter in the bar model from \citet{2022MNRAS.513..768C}, we allow the moment
of inertia of the bar to vary with ${\RCR}^2$. To be more precise, we allow
\begin{equation}
I = \frac{I_6}{10^{10} \Msun (\kms)^2} \left( \frac{\RCR}{6\,\textrm{kpc}} \right)^2\textrm{,}
\end{equation}
where $I_6$ is a free parameter chosen by the user. We found that allowing $I_6=8$ is a good approximation to our bar model.

In addition to $I_6$, we allowed for another free parameter - the torque from
the gas phase on the bar, $\tau_{\textrm{gas}}$. This torque is applied to the
bar in the same way as the torque from the halo is applied. The torque is given
in code units ($10^{10}\Msun \left(\kms\right)^2$). We allow this torque to
mildly vary with pattern speed according to the formula,
\begin{equation}
\tau = \tau_{\textrm{gas}} + (40\,\kms/\textrm{kpc} - \Omega_p)\textrm{.}
\end{equation}
We are motivated to do this because of our result in Appendix~\ref{app:varyps}
which shows that more slowly rotating bars have higher gas infall rates and thus
larger positive torques. In the $\tau_{\textrm{gas}}=0$ case, we do not allow
the gas torque to vary with pattern speed.

We show the effect of varying the gas torque $\tau_{\textrm{gas}}$ from $0$ to
$20$ in increments of $2$ in Fig.~\ref{fig:sam}. The solid lines indicate the
semi-analytic model, while the two dashed lines correspond to our fiducial
simulations introduced earlier. For reference, the average torque exerted by the
gas phase on the bar in our fiducial simulation was $11.7$ in code units. We see in Fig.~\ref{fig:sam} that we can reproduce the stability of our fiducial
gas disk simply by including a positive torque on the order of $6$. Our
semi-analytic model with no gas torque can reproduce the pattern speed evolution
of the $N$-body case.

We next take the $\tau_{\textrm{gas}}=0$ and $20$ cases from Fig.~\ref{fig:sam}
and plot the torque evolution. This result, given in Fig.~\ref{fig:sam-torque},
is comparable to the lower panel of Fig.~\ref{fig:prop}. We find that the
$\tau_{\textrm{gas}}=0$ case compares favorably to the \Nbody{} case described
in previous sections. The bar exerts a steady negative torque in this case (blue
line). When a gas torque is included (orange lines), we find that the halo's
torque becomes much weaker, similar to what we found in the SMUGGLE case. The
gas applies a steady positive torque by construction. The exhaustion process is
reproduced in our simple semi-analytic model.

@@

First, we note that \citet{2020MNRAS.491.3655G} found that the rotation
parameter \Rot{} positively correlates with gas fraction, such that galaxies
with higher gas fractions are rotating more slowly. However, it is not obvious
this is in tension with our result since the gas fraction of galaxies correlates
with other galactic properties \citep{2009ARAA..47..159B}. Furthermore, the
measurement of pattern speeds is a delicate process still prone to large errors.
\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/ps_late_start.pdf}
    \caption{Pattern speed evolution with a lower initial pattern speed. We
    tested the evolution of our system when gas is added to the \Nbody{} run at
    a later time, but with all other simulation parameters kept the same. The
    setup is therefore identical to our previous runs just with a bar that is
    larger, stronger, and with a lower pattern speed. We find that the pattern
    speed evolution is very similar to our fiducial case, except that the bar
    retains its original pattern speed. This indicates a mechanism which keeps
    the bar at its formation pattern speed, and that there is not a particular
    pattern speed which the system tends to.}
    \label{fig:snap700}
\end{figure}

@@

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F}. However,
the pattern speeds of bars in both cosmological simulations and the real
universe can be affected by environmental processes not included in our
simulation -- e.g., satellite infall \citep{2011Natur.477..301P}, non-sphericity
\citep{2013MNRAS.429.1949A}, rotation in the dark matter halo
\citep{2013MNRAS.434.1287S, 2014ApJ...783L..18L, 2018MNRAS.476.1331C,
2019MNRAS.488.5788C}, or perhaps even the gaseous circumgalactic medium.
Naturally, extending our present work to account for such effects is a crucial
next step in understanding the formation and evolution of galactic bars.

@@

\section{Conclusions}
\label{sec:conclusions}
The implications of our findings are numerous. First, we naturally explain why
nearly all observed galaxies are fast rotators without requiring the inner
regions of dark matter halos to be underdense \citep{1998ApJ...493L...5D,
2000ApJ...543..704D} or requiring new physics \citep{2021MNRAS.503.2833R,
2021MNRAS.508..926R}. Second, we show that the role of gas is of paramount
importance in studies which attempt to uncover the nature of dark matter from
its effect of slowing down the bar \citep{2021MNRAS.500.4710C,
2021MNRAS.505.2412C}. Third, we provide an explanation for how the Milky Way's
bar could be both long-lived and a fast rotator, of which there is some
observational evidence \citep{2019MNRAS.490.4740B}. And finally, we complicate
the picture of radial mixing expected to sculpt the Milky Way's disk
\citep{2012MNRAS.420..913B, 2015ApJ...808..132H}, a process which relies upon
the pattern speed of the bar to change with time Our work does not alter
expectations for radial mixing induced by spiral arms
\citep{2002MNRAS.336..785S}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=9cm]{fig/torque_ps.pdf}
    \caption{Average torque exerted by gas on a bar which rotates at a fixed
    pattern speed. Since only gas within the corotation radius is able to infall
    and slower bars have larger corotation radii, slower bars experience a
    larger net torque than faster bars. The setup of the simulations used here
    is identical to the SMUGGLE case discussed earlier, except the \Nbody{} disk
    is rotated as a solid body with a constant angular
    velocity.}
    \label{fig:equil}
\end{figure}

@@

>>>>

% Abstract of the paper
\begin{abstract}
Elongated bar-like features are ubiquitous in galaxies, occurring at the centers
of approximately two-thirds of spiral disks.  Due to gravitational interactions
between the bar and the other components of galaxies, it is expected that
angular momentum and matter will redistribute over long (Gyr) timescales in
barred galaxies. Previous work ignoring the gas phase of galaxies has
conclusively demonstrated that bars should slow their rotation over time due to
their interaction with dark matter halos. We have performed a simulation of a
Milky Way-like galactic disk hosting a strong bar which includes a
state-of-the-art model of the interstellar medium and a live dark matter halo.
In this simulation the bar pattern does not slow down over time, and instead
remains at a stable, constant rate of rotation. This behavior has been observed
in previous simulations using more simplified models for the interstellar gas,
but the apparent lack of secular evolution has remained unexplained. We propose
that the gas phase of the disk and the dark matter halo act in concert to
stabilize the bar pattern speed and prevent the bar from slowing down or
speeding up. We find that in a Milky Way-like disk, a gas fraction of only about
5\% is necessary for this mechanism to operate. Our result naturally explains
why nearly all observed bars rotate rapidly and is especially relevant for our
understanding of how the Milky Way arrived at its present state.
\end{abstract}

@@

We have performed a simulation of a disk galaxy using the finite-volume,
gravito-hydrodynamics code \AREPO{} \citep{2010MNRAS.401..791S}. We use the galaxy
formation model Stars and MUltiphase Gas in GaLaxiEs
\citep[SMUGGLE;][]{2019MNRAS.489.4233M}. This disk galaxy exhibits almost no
evolution in the bar pattern speed over several Gyr when the gas phase is
accounted for and properly modeled. This behavior has been observed in a few
previous works \citep{1993AA...268...65F, 2010ApJ...719.1470V,
2014MNRAS.438L..81A}. However, we are the first to demonstrate that the behavior
ought to be present in a large fraction of galaxies, since it occurs in our
simulation with gas fractions as low as about $5\%$. We are also the first to
provide a physical explanation of the behavior with clear observational
predictions.

@@

As we saw qualitatively in Fig.~\ref{fig:overview}, the upper panel of
Fig.~\ref{fig:strength} shows that the length of the bar in the \Nbody{} case
grows over time while it remains roughly constant in the SMUGGLE case. This is
also consistent with previous numerical work, which found that bars tend to grow
as they slow down and the radius of corotation increases
\citep{2000ApJ...543..704D, 2003MNRAS.341.1179A}. The time evolution of the bar
strength, defined as the maximum of $\left|A_2/A_0\right|$ as a function of
radius, is shown in the lower panel of Fig.~\ref{fig:strength}. The quantity
$\left|A_2/A_0\right|$ varies from $0$ to $1$, with larger values indicating a
stronger bar pattern. We see that in the \Nbody{} case, $\left|A_2/A_0\right|$
increases over time as the bar pattern slows. This is consistent with previous
\Nbody{} simulations which showed a clear correlation between the bar pattern
speed and the bar strength \citep[e.g.,][]{2003MNRAS.341.1179A}. In the SMUGGLE
case, we see that the bar strength has an initial drop but then remains at a
roughly constant, but slightly decreasing, strength. This is consistent with the
pattern speed in the SMUGGLE case being roughly constant or slightly increasing.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Pattern Speed Evolution}
The lack of evolution in the pattern speed of the SMUGGLE case (seen in
Fig.~\ref{fig:prop}) is intimately tied to the sudden decrease in torque exerted
on the bar by the dark matter halo. We argue that this can be understood in
terms of the halo wake mechanism. In the \Nbody{} case, halo material that is
resonant with the bar will form a wake which lags behind and exerts a negative
torque on the bar, slowing it down \citep{1984MNRAS.209..729T,
1985MNRAS.213..451W, 1992ApJ...400...80H}.\footnote{Since the bar is not a solid
body, it is not guaranteed that a negative torque will slow it down - e.g. a
negative torque could shred the bar, reducing its moment of inertia without
changing its pattern speed. However, the bar seems to empirically respond to a
negative torque induced by a halo wake by slowing down.} As the bar slows down,
the location of the resonances in phase space changes, allowing halo material
newly resonant with the bar to participate in forming the wake. However, the gas
is a reliable source of positive torque on the bar, speeding the bar up. This
stops the resonance location from changing such that the halo cannot reinforce
the wake, arresting the process by which the halo can slow the bar down. We term
this process ``halo exhaustion.''

@@

We argue that the following occurs. First, the bar is not able to slow down
quickly enough due to the positive torque of the infalling gas. This causes
the resonant halo phase space at a particular pattern speed, $\Omega_{\textrm{p},0}$,
to become exhausted and no longer able to support a negative torque. Second,
the gas is still exerting a positive torque on the bar, and therefore the
pattern speed will again increase. Since at higher pattern speeds the halo has
not yet been totally exhausted, the halo will once again be able to exert a
negative torque on the bar. The pattern speed will then settle at a new value
slightly higher than $\Omega_{\textrm{p},0}$ where the gas and halo torques cancel.
Over time, the pattern speed should slowly increase as the halo becomes
progressively exhausted.

@@

\subsection{Varying Initial Gas Fractions}
We performed a test in which we varied the initial gas fraction of the
disk. In our fiducial run, we set the surface density of the gas disk from
$4\,\textrm{kpc}$ to $\sim9.3\,\textrm{kpc}$ to be $20\,\Msun/\textrm{pc}^2$.
We also ran with surface densities of $15$, $10$, and
$5\,\Msun/\textrm{pc}^2$. These correspond to initial gas fractions of
approximately $16\%$, $10\%$, $7\%$, and $4\%$. The pattern speed evolution is
shown in Fig.~\ref{fig:fgas} We find that the bar in disks with
initial surface densities of $20$, $15$, and $10\,\Msun/\textrm{pc}^2$ evolve
with a constant pattern speed while the bar in a disk with initial surface
density of $5\,\Msun/\textrm{kpc}^2$ slows down at a similar rate to the \Nbody{} case.

@@

\subsection{Smooth Interstellar Medium}
We performed a simulation of the same disk but with a simpler model of the
interstellar medium \citep{2003MNRAS.339..289S}, closer to standard methods used
in cosmological simulations of galaxy formation and described in more detail in
Section~\ref{sec:methods}. The result of this test is presented in
Fig.~\ref{fig:GFM}. We find that the pattern speed evolution is nearly the same
in this case, and so conclude that our result is not sensitive to the details of
the model for the interstellar medium.

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/ps_late_start.pdf}
    \caption{Pattern speed evolution with a lower initial pattern speed. We
    tested the evolution of our system when gas is added to the \Nbody{} run at
    a later time, but with all other simulation parameters kept the same. The
    setup is therefore identical to our previous runs just with a bar that is
    larger, stronger, and with a lower pattern speed. We find that the pattern
    speed evolution is very similar to our fiducial case, except that the bar
    retains its original pattern speed. This indicates a mechanism which keeps
    the bar at its formation pattern speed, and that there is not a particular
    pattern speed which the system tends to.}
    \label{fig:snap700}
\end{figure}

@@

We allow the bar in this model to rotate as a solid body. However, we crucially
allow the pattern speed of the bar to freely change with time in accordance with
the torque exerted on the dark matter halo by the bar. In particular, we
subtract the $z$-component of this torque divided by the moment of inertia of
the bar from the pattern speed at each timestep. Since the radius of corotation
\RCR{} is a parameter in the bar model from \citet{2022MNRAS.513..768C}, we
allow the moment of inertia of the bar to vary with ${\RCR}^2$. To be more
precise, we allow
\begin{equation}
I = \frac{I_6}{10^{10} \Msun (\kms)^2} \left( \frac{\RCR}{6\,\textrm{kpc}} \right)^2\textrm{,}
\end{equation}
where $I_6$ is a free parameter chosen by the user. We found that allowing
$I_6=8$ is a good approximation to our fiducial disk model.

In addition to $I_6$, we allowed for another free parameter - the torque from
the gas phase on the bar, $\tau_{\textrm{gas}}$. This torque is applied to the
bar in the same way as the torque from the halo is applied. The torque is given
in code units ($10^{10}\Msun \left(\kms\right)^2$). We allow this torque to
mildly vary with pattern speed according to the formula,
\begin{equation}
\tau = \tau_{\textrm{gas}} + (40 - \Omega_{\textrm{p}})\textrm{,}
\end{equation}
where $\Omega_{\textrm{p}}$ is given in $\kms/\textrm{kpc}$. We are motivated to
do this because of our result in Appendix~\ref{app:varyps} which shows that more
slowly rotating bars have higher gas infall rates and thus larger positive
torques. In the $\tau_{\textrm{gas}}=0$ case, we do not allow the gas torque to
vary with pattern speed.

We show the effect of varying the gas torque $\tau_{\textrm{gas}}$ from $0$ to
$20$ in increments of $2$ in Fig.~\ref{fig:sam}. The solid lines indicate the
semi-analytic model, while the two dashed lines correspond to our fiducial
simulations introduced earlier. For reference, the average torque exerted by the
gas phase on the bar in our fiducial simulation was $11.7$ in code units. We see
in Fig.~\ref{fig:sam} that we can reproduce the stability of our fiducial gas
disk (i.e., its lack of secular evolution) simply by including a positive torque
on the order of $6$. Our semi-analytic model with no gas torque can reproduce
the pattern speed evolution of the $N$-body case.

We next take the $\tau_{\textrm{gas}}=0$ and $20$ cases from Fig.~\ref{fig:sam}
and plot the torque evolution. This result, given in Fig.~\ref{fig:sam-torque},
is comparable to the lower panel of Fig.~\ref{fig:prop}. We find that the
$\tau_{\textrm{gas}}=0$ case compares favorably to the \Nbody{} case described
in previous sections. The bar exerts a steady negative torque in this case (blue
line). When a gas torque is included (orange lines), we find that the halo's
torque becomes much weaker, similar to what we found in the SMUGGLE case. The
gas applies a steady positive torque by construction. Therefore, the exhaustion
process is reproduced in our simple semi-analytic model.

@@

First, we note that \citet{2020MNRAS.491.3655G} found that the rotation
parameter \Rot{} positively correlates with gas fraction, such that galaxies
with higher gas fractions are rotating more slowly. However, it is not obvious
this is in tension with our result since the gas fraction of galaxies correlates
with other galactic properties \citep{2009ARAA..47..159B}. Furthermore, the
measurement of pattern speeds is a delicate process still prone to large errors.

@@

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F}. However,
the pattern speeds of bars in both cosmological simulations and the real
universe can be affected by environmental processes not included in our
simulation -- e.g., satellite infall \citep{2011Natur.477..301P}, non-sphericity
\citep{2013MNRAS.429.1949A}, rotation in the dark matter halo
\citep{2013MNRAS.434.1287S, 2014ApJ...783L..18L, 2018MNRAS.476.1331C,
2019MNRAS.488.5788C}, or perhaps even the gaseous circumgalactic medium.
Naturally, extending our present work to account for such effects is a crucial
next step in understanding the formation and evolution of galactic bars. We are
presently engaged in such an exploration.

@@

\section{Conclusions}
\label{sec:conclusions}
We performed a simulation of a Milky Way-like galactic disk hosting a strong bar
with a state-of-the-art model for the interstellar medium. We found that the
pattern speed of the bar in this simulation does not slow down but rather
remains at a stable, constant pattern speed. We provided a simple semi-analytic
model which reproduces many of the features from our fiducial disk model.

The implications of our findings are numerous. First, we naturally explain why
nearly all observed galaxies are fast rotators without requiring the inner
regions of dark matter halos to be underdense \citep{1998ApJ...493L...5D,
2000ApJ...543..704D} or requiring new physics \citep{2021MNRAS.503.2833R,
2021MNRAS.508..926R}. Second, we show that the role of gas is of paramount
importance in studies which attempt to uncover the nature of dark matter from
its effect of slowing down the bar \citep{2021MNRAS.500.4710C,
2021MNRAS.505.2412C}. Third, we provide an explanation for how the Milky Way's
bar could be both long-lived and a fast rotator, of which there is some
observational evidence \citep{2019MNRAS.490.4740B}. And finally, we complicate
the picture of radial mixing expected to sculpt the Milky Way's disk
\citep{2012MNRAS.420..913B, 2015ApJ...808..132H}, a process which relies upon
the pattern speed of the bar to change with time Our work does not alter
expectations for radial mixing induced by spiral arms
\citep{2002MNRAS.336..785S}.

@@

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/torque_ps.pdf}
    \caption{Average torque exerted by gas on a bar which rotates at a fixed
    pattern speed. Since only gas within the corotation radius is able to infall
    and slower bars have larger corotation radii, slower bars experience a
    larger net torque than faster bars. The setup of the simulations used here
    is identical to the SMUGGLE case discussed earlier, except the \Nbody{} disk
    is rotated as a solid body with a constant angular
    velocity.}
    \label{fig:equil}
\end{figure}

@@

We integrated our model for $5\,\textrm{Gyr}$ with a timestep of
$0.01\,\textrm{Gyr}$.
